Bayesian Neural Networks

### 2024-04-02 Paper/paper.tex
Updated notebook

		% Connections with weights
		\draw[->] (input1) -- node[weight, above] {$w_{1,1}$} (hidden1);
		\draw[->] (input2) -- node[weight, above] {$w_{2,1}$} (hidden1);
		\draw[->] (input1) -- node[weight, right] {$w_{1,2}$} (hidden2);
		\draw[->] (input2) -- node[weight, right] {$w_{2,2}$} (hidden2);
		\draw[->] (input1) -- node[weight, above] {$w_{1,3}$} (hidden3);
		\draw[->] (input2) -- node[weight, above] {$w_{2,3}$} (hidden3);
		\draw[->] (hidden1) -- node[weight, right] {$v_{1,1}$} (output1);
		\draw[->] (hidden2) -- node[weight, right] {$v_{2,1}$} (output1);
		\draw[->] (hidden3) -- node[weight, right] {$v_{3,1}$} (output1);
		\draw[->] (hidden1) -- node[weight, above] {$v_{12}$} (output2);
		\draw[->] (hidden2) -- node[weight, above] {$v_{2,2}$} (output2);
		\draw[->] (hidden3) -- node[weight, above] {$v_{3,2}$} (output2);
	\end{tikzpicture}
	\caption{Example neural network}
\end{figure}

Neural networks....

Neural networks are made out of a series of neurons. 
\begin{figure}[H]
	\centering
	\begin{tikzpicture}[
		neuron/.style={
			circle,
			draw,
			minimum size=1.5em,
			inner sep=0pt,
		},
		font=\footnotesize,
		>=latex
		]
		% Draw the neuron
		\node [neuron] (neuron) at (0,0) {$\Sigma$};
		% Draw the input nodes and labels
		\foreach \i/\txt in {1/$x_1$,2/$x_2$,3/$x_n$} {
			\node [neuron,left=of neuron] (input\i) at (-1.5,-\i +2) {\txt};
			\draw[->] (input\i) -- node[above] {} (neuron);
		}
		% Draw the bias node and label
		\node [neuron,left=of neuron] (bias) at (1.25,1) {Bias};
		\draw[->] (bias) -- node[right] {} (neuron);
		% Draw the activation function label
		\node[align=center,below right =0.5em of neuron] {Activation \\ function};
		% Draw the output node and label
		\node [neuron,right=of neuron] (output) at (1.5,0) {Output};
		\draw[->] (neuron) -- node[above] {} (output);
		% Draw the relevant functions
		%\draw[->] (0,-1.5) -- (0,-2.5) node[midway,right] {Weighted sum};
		%\draw[->] (-1.5,-3.5) -- (-1.5,-4.5) node[midway,left] {Bias};
		%\draw[->] (1.5,-0.5) -- (1.5,-1.5) node[midway,right] {Activation};

@@

	\end{tikzpicture}
	\caption{Neural network neuron}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=.8\textwidth]{../Images/big-pic-cnn.jpg}
	\caption{CNN pipeline \cite{eli5CNN}}
\end{figure}

Convolutional neural networks (CNN) are a type of neural network that is better suited for image recognition. Instead of reading the entire image a CNN slides over the image...

The result is that the neural network trains faster..

@@

\subsection{Bayesian Conolutional Neural Networks}

Same principle...

@@

The CIFAR-10 dataset...

@@

We used the following hyperparamaters for training
	\begin{center}
		\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
			\hline
			\textbf{Hyperparameter} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
			\hline\hline
			Epochs & 500 & 500\\
			\hline
			Learning Rate & ....  & May be higher (0.01 - 0.1) due to simpler structure  \\
			\hline
			Regularization & L1/L2 weight decay or Dropout common to prevent overfitting & Can benefit from Dropout, but weight decay might be less crucial \\
			\hline
			Optimizer & Adamw  & Adamw  \\
			\hline
		\end{tabular}
	\end{center}

@@

>>>>

		% Connections with weights
		\draw[->] (input1) -- node[weight, above] {$w_{1,1}$} (hidden1);
		\draw[->] (input2) -- node[weight, above] {$w_{2,1}$} (hidden1);
		\draw[->] (input1) -- node[weight, right] {$w_{1,2}$} (hidden2);
		\draw[->] (input2) -- node[weight, right] {$w_{2,2}$} (hidden2);
		\draw[->] (input1) -- node[weight, above] {$w_{1,3}$} (hidden3);
		\draw[->] (input2) -- node[weight, above] {$w_{2,3}$} (hidden3);
		\draw[->] (hidden1) -- node[weight, right] {$v_{1,1}$} (output1);
		\draw[->] (hidden2) -- node[weight, right] {$v_{2,1}$} (output1);
		\draw[->] (hidden3) -- node[weight, right] {$v_{3,1}$} (output1);
		\draw[->] (hidden1) -- node[weight, above] {$v_{12}$} (output2);
		\draw[->] (hidden2) -- node[weight, above] {$v_{2,2}$} (output2);
		\draw[->] (hidden3) -- node[weight, above] {$v_{3,2}$} (output2);
	\end{tikzpicture}
	\caption{Example neural network}
	\label{fig:example-nn}
\end{figure}

A neural network takes a series of inputs... In figure \ref{fig:example-nn}, the network takes two inputs, has one hidden layer of size

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[
		neuron/.style={
			circle,
			draw,
			minimum size=1.5em,
			inner sep=0pt,
		},
		font=\footnotesize,
		>=latex
		]
		% Draw the neuron
		\node [neuron] (neuron) at (0,0) {$\Sigma$};
		% Draw the input nodes and labels
		\foreach \i/\txt in {1/$1$,2/$2$,3/$n$} {
			\node [neuron,left=of neuron] (input\i) at (-1.5,-\i +2) {x\txt};
			\draw[->] (input\i) -- node[above] {$w$\txt} (neuron);
		}
		% Draw the bias node and label
		\node [neuron,left=of neuron] (bias) at (1.25,1) {Bias};
		\draw[->] (bias) -- node[right] {} (neuron);
		% Draw the activation function label
		\node[align=center,below right =0.5em of neuron] {Activation \\ function};
		% Draw the output node and label
		\node [neuron,right=of neuron] (output) at (1.5,0) {Output};
		\draw[->] (neuron) -- node[above] {} (output);
		% Draw the relevant functions
		%\draw[->] (0,-1.5) -- (0,-2.5) node[midway,right] {Weighted sum};
		%\draw[->] (-1.5,-3.5) -- (-1.5,-4.5) node[midway,left] {Bias};
		%\draw[->] (1.5,-0.5) -- (1.5,-1.5) node[midway,right] {Activation};

@@

	\end{tikzpicture}
	\caption{Neural network neuron}
	\label{fig:neuron}
\end{figure}

Neural networks are made out of a series of neurons... The neurons take a set of inputs, multiplies the inputs by the weights, sums the weighted input, adds a bias, and runs the output through an activation function...

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=.8\textwidth]{../Images/big-pic-cnn.jpg}
	\caption{CNN pipeline \cite{eli5CNN}}
	\label{fig:cnn-pipeline}
\end{figure}

Convolutional neural networks (CNN) are a type of neural network that is better suited for image recognition. While this might sound like a seperate model structure, CNNs are largely the same. In figure \ref{fig:cnn-pipeline} the difference between a traditional neural network is the convolutional layer. Instead of reading the entire image at once, a convolutional layer slides over the image...

IMAGE OF SLIDING (gif split)

 ...

@@

\subsection{Bayesian Convolutional Neural Networks}

Bayesian convolutional neural network (BCNN) are similar to CNNs. The difference between is that BCNNs and a CNN is that the BCNN uses a bayesian neuron.

@@

The CIFAR-10 ((Canadian Institute For Advanced Research 10) dataset is a machine learning benchmarking set. It contatins 60,000 $16 \times 16$ RGB pictures of: airplanes, cars, birds, cats, deer, dogs, frogs, horses, ships, and trucks\cite{cifar10}. It is used...

@@

We used the following hyperparamaters for training:
\begin{figure}[H]
	\begin{center}
	\begin{tabular}{|c||p{3cm}|p{3cm}|} % Adjust p{width} as needed
		\hline
		\textbf{Hyperparameter} & \textbf{CNN} & \textbf{BCNN} \\ [0.5ex] 
		\hline\hline
		Epochs & 500 & 500\\
		\hline
		Learning Rate & ....  & May be higher (0.01 - 0.1) due to simpler structure  \\
		\hline
		Regularization & L1/L2 weight decay or Dropout common to prevent overfitting & Can benefit from Dropout, but weight decay might be less crucial \\
		\hline
		Optimizer & Adamw  & Adamw  \\
		\hline
	\end{tabular}
\end{center}
\end{figure}

In addition to the above, the two models have the same number of levels...

@@

The two have roughly similar accuracies given the model
